COG-ED Manuscript

### 2022-03-03 06_Paper/COG-ED/Manuscript.Rmd
Update Manuscript.Rmd
finalized sample size calculation

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.

@@

Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
As there was no prior evidence on the magnitude of an interaction between *n*-back level and NFC, we assumed a small to medium effect size of $f=.175$.
Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] for a repeated measures ANOVA with within-between interaction indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
The power analyses of all other hypotheses yielded smaller necessary sample sizes.
To account for technical errors and exclusions of physiological data of the second lab session due to excessive noise, we aim to collect data of 80 participants.

>>>>

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [cf. @Simmons2012].
The paradigm was written and presented using *Psychopy* [@Peirce2019].
We used *R* with *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *afex* [@Singmann2021] and *BayesFactor* [@Morey2021] for all our analyses.

@@

Sample size determination was mainly based on the results of the analyses of Westbrook et al. [-@Westbrook2013] (see [Design Table](#DesignTableSection)).
The hypothesis that yielded the largest necessary sample size was a repeated measures ANOVA with within-between interaction of NFC and *n*-back level influencing SVs.
Sample size analysis with *G\*Power* [@Faul2007; @Faul2009] indicated that we should collect data from at least 72 participants, assuming $\alpha=.05$ and $\beta=.95$.
However, the sample size analysis for the hypotheses of the second lab session revealed a larger necessary sample size of 85 participants to find an effect of $d=-0.32$ of emotion regulation on facial muscle activity with $\alpha=.05$ and $\beta=.95$.
To account for technical errors, noisy physiological data, or participants who indicate that they did not follow the instructions, we aim to collect about $50\%$ more data sets than necessary, $N=120$ in total.
